---
title: "ceceg27_PeerCommentary_aer13_05"
author: "Abby_Robinson"
date: "11/16/2021"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

[1] Using the “KamilarAndCooperData.csv” dataset, run a linear regression looking at log(HomeRange_km2) in relation to log(Body_mass_female_mean) and report your β oeffiecients (slope and intercept).

### First we need to load in the data 
```{r}
library(curl)
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN588_Fall21/KamilarAndCooperData.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
```
### Looks good, now lets get the data ready to work with 
```{r}
hr<-e$HomeRange_km2
bmf<-e$Body_mass_female_mean #shorten the variable names (just makes things easier)
```

Abby: this code isn't working for me, I think you named your data "d", so you should use "d" here instead of "e"

```{r}
hr<-d$HomeRange_km2
bmf<-d$Body_mass_female_mean #shorten the variable names (just makes things easier)
```

### Preforming the linear regression, making sure to log each variable, and reporting the values
```{r}
reg <- lm(log(hr) ~ log(bmf), data = d, na.action=na.exclude) #removing nas just in case
reg 
plot(reg) #normal looking qq plot
#Intercept (B0) is -9.75, slope (B1) is 1.087 (I think I'm reading the output right but these two values could be reversed)
```
Abby: I got slightly different numbers when I ran your code 
Abby: your "na.action=na.exclude" code here seems very useful! I had to exclude NAs to get my bootstrapping to work, but I did it separately. This seems more efficient 

### Finding the confidence intervals
```{r}
confint(reg, level =.95)
#Intervals are: -13.41 and -6.09 for intercept; .67 and 1.5 for long(bmf)
```

Abby: these are not the numbers I am seeing in your output. I see: 

                  2.5 %    97.5 %
(Intercept) -10.7720889 -8.110374
log(bmf)      0.8685707  1.204292

Abby: not sure what the problem could be here 

[2] Then, use bootstrapping to sample from your data 1000 times with replacement, each time fitting the same model and calculating the same coefficients. This generates a sampling distribution for each β coefficient.

### first I'll make the bootstrap 
```{r}
library(boot)
?boot()
#I think boot will work, but I'll need to make a function first
bootstrap <-function(data, indicies) {
  line <-lm(data =d, log(hr) ~ log(bmf))
  d <- data [indicies, ]
  return (coef(line))
}

result <- boot(d, statistic=bootstrap, R=1000)
result
# getting t1 = -9.75 and t2 = 1.087, the same numbers as above, so the SE is the same for both the regression and the bootstrap!
```
Abby: Are you supposed to get the same exact numbers in your regression model and bootstrap? When I encountered this in my first attempt at the homework, I thought it meant that my sample distribution wasn't working properly because there should be a little random variation in the output of the different models? But, idk, I am not sure 

```{r}
?boot.ci() #this works with the boot command 

boot.ci(boot.out=result, type = "norm")
#it doesn't seem like this is working, I get an answer of -9.75 and -9.75 which just doesn't feel right
#Now that I'm thinking about it this could be right, each T1 value is -9.75 in the 1000 samples, so it makes sense that the confidence interval would be super small or basically nonexistant 
```
Abby: I used quantile() to get my confidence intervals, but I didn't use the boot package so that might not be very useful for you 

How does the former compare to the SE estimated from your entire dataset using the formula for standard error implemented in lm()?

## The standard errors seem to be the same for both the lm and the bootstrap: t1 or B0 = -9.75, and t2 or b1 = 1.087

How does the latter compare to the 95% CI estimated from your entire dataset?

## For B0, the confidence interval is smaller than that of the lm. I haven't been able to figure out how to get the CI for B1 using bootstrap. I need to look further into it. 

Challenges 
1. I am not 100% confident in my bootstrap, particularly the confidence interval bit. 
2. I haven't been able to get a CI value for B1 for the bootstrap. 
3. I don't even know where to begin with the extra credit. I will try it out if I have time this week.  

